\chapter{Conclusions}
\protect\label{chapter:conclusions}
\lhead{Chapter \ref{chapter:conclusions} \emph{Conclusions}}

This {\paperorthesis} has set out to study measurements of periodicity via measurements of the {\ha} line in particular
and focusing on \prox.

A study of photometric measurements from {\asas} and {\hst} produced clear evidence of a rotation period of 82.6 $\pm$
0.1 days with negligible FAP. This produced a benchmark from which to evaluate spectroscopic measurements including that
of equivalent width and the virtually identical {\ha} Index, which were applied to the {\ha} line to demonstrate that
they did not prove able, in terms of reliable recovery of the period at all or with an acceptable error bar, to deliver
a result in isolation, certainly as far as {\prox} is concerned. The measurement of lines presented in this
\paperorthesis, the peak ratio, appears to be consistently better than other measurements and is particularly suitable
for {\ha} line profiles such as that for \prox, which have a ``horned'' appearance with two \horn s around a relatively
unchanging central minimum.

A look at simple 2D models enabled the variations of equivalent widths to be reproduced and the validity of the methods
of period recovery to be established to a reasonable degree including in the face of varying SNR levels and simulated
flares. However the models were ``too good'' for equivalent width whilst ``not good enough'' for peak ratios. The need
for a more sophisticated 3D model with vertical motion is clear if the activity in \prox, probably other late \rdwarf s
with lower rotation period but relatively high activity, are to be understood. It seems likely, however, that these
methods will be of value for analysing spectra of faster rotating stars.

\examrevision{It was clear from the studies in Section \ref{section:asasfap} that many more observations, approaching
  the numbers from {\asas}, are necessary to express confidence in periodicity results. On the other hand, it was also
  clear from the modelling that signal to noise ratios down to about 20 do not disturb the results appreciably, even in
  the presence of flares.}

In this process, however, as well as establishing the rotation period of {\prox} \examrevision{with a reasonable degree
  of confidence,} a recent alternative assessment of the rotation period as 116.6 days was clearly discounted as a false
positive.
